---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# milcao

<!-- badges: start -->

[![R-CMD-check](https://github.com/srvaldivia/milcao/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/srvaldivia/milcao/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

The goal of milcao is to provide handy functions to handle geospatial data and tools to improve some GIS workflow and analysis.

## Installation

You can install the development version of milcao from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("srvaldivia/milcao")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(milcao)
data_directory <- system.file("extdata", package = "milcao")
```

The function `find_shapes()` can be used to know all the existing Shapefiles within a given directory using its path.

```{r}
find_shapes(path = data_directory)
```

By default `find_shapes()` does not search Shapefiles living in any subfolder inside the folder path. However, this can be changed setting `subfolders = TRUE`.

```{r}
 find_shapes(path = data_directory, subfolders  = TRUE)
```

Notice that the default behaviour of `find_shapes()` is set to return only the name of every Shapefile. You can add the argument `full = TRUE` to get the full path to each Shapefile.

```{r}
find_shapes(path = data_directory, subfolders  = TRUE, full = TRUE)
```
